### 2023-11-10 Scripts/Manuscript/manuscript.Rmd
fixed a couple rendering issues

# adding an asterix for significance to the significant p in the dataframe
H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "^*")

@@

# print the table in apa formatting
apa_table(
  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
  , caption = "Model Results from Tests of Hypothesis 3"
  , note = "The Cronbach's alpha section shows the models where the calculated Cronbach's alpha coefficient was the independent variable. In the Omega section it was the calculated omega coefficient. The random slope model for Cronbach's alpha did not converge, thus it results are not shown here. $^* p < .05$"
  , escape = FALSE, placement= "ht", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))

@@

Plot_456_2

>>>>

# adding an asterix for significance to the significant p in the dataframe
H3_table_dataframe[3,5] <- paste0(H3_table_dataframe[3,5], "$^*$")

@@

# print the table in apa formatting
apa_table(
  H3_table_for_printing, align = c("l", "r", "r", "r", "r")
  , caption = "Model Results from Tests of Hypothesis 3"
  , note = "The Alpha and Omega sections show the models where the independent variable was the calculated Cronbach's alpha and omega coefficient respectively. The random slope model for Cronbach's alpha did not converge, thus it results are not shown here. $^* p < .05$"
  , escape = FALSE, placement= "ht", midrules = c(1, 2, 5, 7, 8, 9, 12, 15))

@@
